---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# polypack

<!-- badges: start -->
[![R-CMD-check](https://github.com/joseailton100224/polypack/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/joseailton100224/polypack/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/joseailton100224/polypack/branch/main/graph/badge.svg)](https://app.codecov.io/gh/joseailton100224/polypack?branch=main)
[![ORCiD:0000-0001-7414-1154](https://img.shields.io/badge/ORCiD-0009--0003--5992--6019-A6CE39?logo=ORCID&colorIcon.svg)](https://orcid.org/0009-0003-5992-6019)
<!-- badges: end -->

O objetivo do pacote é construir uma tabela frequência de uma variável de um data frame.

## Installation

You can install the development version of polypack from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joseailton100224/polypack")
```

## Example

Este é um exemplo básico que mostra como construir a tabela de frequência a partir de um
data frame:

```{r example}
library(polypack)
## basic example code

tabela_frequencia(mb$Estatist.)

```


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
